stupid backoff

### 2019-11-30 al_stup.Rmd
final version

        if(nrow(obs_trigs) < 1) {
                bigr_probs = getBigProbs(bigPre, bigrams, unigrams)
                probs = data.frame(ngram = bigr_probs$ngram, 
                                   prob = bigr_probs$prob * 0.4)
                return(probs)
        } else {
                probs = obs_trigs %>% rename( prob = freq) %>%
                    mutate(prob = prob / bigr_count) %>% 
                    arrange(desc(prob), ngram)
                return(probs)
        }

>>>>

        if(nrow(obs_trigs) < 1) {
                bigr_probs = getBigProbs(bigPre, bigrams, unigrams)
                probs = data.table(ngram = bigr_probs$ngram, 
                                   prob = bigr_probs$prob * 0.4)
                return(probs)
        } else {
                probs = obs_trigs %>% rename( prob = freq) %>%
                    mutate(prob = prob / bigr_count) %>% 
                    arrange(desc(prob), ngram)
                return(probs)
        }
